\cvsection{Experience}
\vspace{-1em}

\begin{minipage}[t]{.49\linewidth}
    \cvsubsection{\color{awesome-concrete}Academic}
% 
    \begin{cventries}
% 
        \cventryvar
            {PhD in Chemistry}
            {Université Côte d'Azur, France}
            {Institut de Chimie de Nice}
            {2018 -- 2021}
            {
            \begin{cvitems}
                \item{Molecular Basis of Chemosensory Perception}
                \item{Supervised by Dr. Sébastien \textsc{Fiorucci} \& Pr. Serge \textsc{Antonczak}}
                \item{Expertise: Chemoinformatics, Molecular Modeling, Machine Learning, Programming, Chemosensory GPCRs}
            \end{cvitems}
            }
% 
        \cventryvar
            {Internship}
            {Université Côte d'Azur, France}
            {Institut de Chimie de Nice}
            {Feb. -- Jul. 2018}
            {
            \begin{cvitems}
                \item{Development of QSAR models to predict olfactory and gustatory \mbox{properties} of molecules in humans and insects}
                \item{Supervised by S. \textsc{Fiorucci}}
            \end{cvitems}
            }

        \cventryvar
            {Internship}
            {Université de Strasbourg, France}
            {Institut de Science et d'Ingénierie Supramoléculaires}
            {Mar. -- Jun. 2017}
            {
            \begin{cvitems}
                \item{Automation of MD simulations from docking results}
                \item{Calculation of binding affinities to myosin using the MM/PBSA \mbox{approach}}
                \item{Supervised by M. \textsc{Cecchini}}
            \end{cvitems}
            }
% 
        \cventryvar
            {Internship}
            {Université Côte d'Azur, France}
            {Institut de Chimie de Nice}
            {Jun. 2016}
            {
            \begin{cvitems}
                \item{Homology Modeling of Bitter Taste Receptors}
                \item{Supervised by S. \textsc{Fiorucci}}
            \end{cvitems}
            }
% 
    \end{cventries}
% 
\end{minipage}
\begin{minipage}[t]{.02\linewidth}
    \cvsubsection{}
\end{minipage}
% 
\begin{minipage}[t]{.49\linewidth}
    \cvsubsection{\color{awesome-concrete}Professional}
% 
    \begin{cventries}
% 
        \cventryvar
            {Google Summer of Code participant}
            {Remote work}
            {MDAnalysis}
            {Jun. 2020 -- Aug. 2020}
            {
            \vspace{-1.2\baselineskip}
            Developer in charge of the interoperability project between MDAnalysis and RDKit python modules: \vspace{1.2\baselineskip}
            \begin{cvitems}
                \item{Conversion between MDAnalysis atom groups and RDKit molecules.}
                \item{Leverage RDKit functionalities (SMARTS queries, molecular descriptors calculations... etc.) directly from MDAnalysis.}
            \end{cvitems}
            \vspace{1em}
            }
% 
        \cventryvar
            {Technician}
            {Strasbourg, France}
            {Institut de Science et d'Ingénierie Supramoléculaires}
            {Jul. 2017 -- Aug. 2017}
            {
            \begin{cvitems}
                \item{Development of computational chemistry workflows for structure-based virtual screening.}
            \end{cvitems}
            \vspace{1em}
            }
% 
        \cventryvar
            {Summer Replacement Clerk \& Teller}
            {Monaco}
            {Various banks}
            {Summer 2012 -- 2016}
            {
            \begin{cvitems}
                \item{Compagnie Monégasque de Banque, BNP Paribas Wealth \mbox{Management}, \& LCL Banque et Assurance}
                \item{Customer reception, filing, data entry for banking transactions.}
            \end{cvitems}
            \vspace{1em}
            }
% 
    \end{cventries}
% 
\end{minipage}