\cvsection{Peer-reviewed publications}

\begin{cvpublications}{First-author publications:}

	\cvpublication{5}
	{Functional Molecular Switches of Mammalian G Protein-Coupled Bitter-Taste Receptors}
	{Topin J., Bouysset C., Pacalon J., Kim Y., Rhyu M., Fiorucci S. \& Golebiowski, J.}
	{2021}
    {Cell. Mol. Life Sci.}
    {https://rdcu.be/cz1ox}

	\cvpublication{4}
	{ProLIF: a library to encode molecular interactions as fingerprints}
	{Bouysset C. \& Fiorucci S.}
	{2021}
    {J. Cheminformatics}
    {https://doi.org/10.1186/s13321-021-00548-6}

    \cvpublication{3}
	{Reverse chemical ecology in a moth: machine learning on odorant receptors identifies new behaviorally active agonists}
	{Caballero-Vidal G., Bouysset C., Gévar J., Mbouzid H., Nara C., Delaroche J., Golebiowski J., Montagné N., Fiorucci S. \& Jacquin-Joly E.}
	{2021}
    {Cell. Mol. Life Sci.}
	{https://doi.org/10.1007/s00018-021-03919-2}

	\cvpublication{2}
	{Novel Scaffold of Natural Compound Eliciting Sweet Taste Revealed by Machine Learning}
	{Bouysset C., Belloir C., Antonczak S., Briand L. \& Fiorucci S.}
	{2020}
	{Food Chem.}
	{https://doi.org/10.1016/j.foodchem.2020.126864}

	\cvpublication{1}
	{Machine Learning Decodes Chemical Features to Identify Novel Agonists of a Moth Odorant Receptor}
	{Caballero-Vidal G., Bouysset C., Grunig H., Fiorucci S., Montagné N., Golebiowski J. \& Jacquin-Joly E.}
	{2020}
	{Sci. Rep.}
	{https://doi.org/10.1038/s41598-020-58564-9}

\end{cvpublications}

\begin{cvpublications}{Other publications:}

	\cvpublication{4}
	{MDAnalysis 2.0 and beyond: fast and interoperable, community driven simulation analysis}
	{Naughton F. B., Alibay I., Barnoud J., Barreto-Ojeda E., Beckstein O. Bouysset C., Cohen O., Gowers R. J., MacDermott-Opeskin H., Matta M., Melo M. N., Reddy T., Wang L., Zhuang Y.}
    {2022}
	{Biophys. J.}
    {https://doi.org/10.1016/j.bpj.2021.11.1368}

    \cvpublication{3}
	{Recent Smell Loss Is the Best Predictor of COVID-19 Among Individuals With Recent Respiratory Symptoms}
	{Gerkin R. C. and 128 colleagues}
    {2021}
	{Chem. Senses}
    {https://doi.org/10.1093/chemse/bjaa081}

	\cvpublication{2}
	{More Than Smell—COVID-19 Is Associated With Severe Impairment of Smell, Taste, and Chemesthesis}
	{Parma V. and 121 colleagues}
    {2020}
	{Chem. Senses}
    {https://doi.org/10.1093/chemse/bjaa041}

    \cvpublication{1}
	{Metal Ions Activate the Human Taste Receptor TAS2R7}
	{Wang Y., Soohoo A. L., Lei W., Christensen C., Margolskee R. F., Bouysset C., Golebiowski J., Zhao H., Fiorucci S. \& Jiang P.}
    {2019}
	{Chem. Senses}
    {https://doi.org/10.1093/chemse/bjz024}

\end{cvpublications}
